\section{Data}

\subsection{Data Source \& Preprocessing}

We base our analysis on an existing `.mobi' file of \infinitejest. This file is put through a `.mobi' to HTML conversion to generate an HTML formatted file as well as a `.mobi' to raw text conversion.

We identify endnote locations in the HTML file using regular expressions. We replace these endnotes with a simplified endnote tag to facilitate later interpolation of the endnote text.

We used \textit{Elegant Complexity} as a resource to find pages with section breaks.~\cite{carlisle_2007} We manually compiled the strings each section started with. We use regular expressions to take these section markers and identify section breaks.

We split the raw text by section and store each one in a separate file; endnotes are also stored in separate files. We remove all inessential special characters (e.g.\ special quotes). We import text files as unicode in our analyses.

\subsection{Named Entitiy Recognition}

Entity recognition and disambiguation pose a significant challenge -- there are more than 200 characters in the novel, and that aliases, pseudonyms, and nicknames are used extensively. 

We utilize the Named Entity Recognition (NER) parser of the Python library SpaCy~\cite{spacy2} augmented with its own Matcher parser.

To create a set of entities, we ran the the library's built in NER model on the text and compared the entities it generated against our own, incrementally built, set. We manually added aliases/pseudonyms to our set of entities based on the candidates the NER model produced. Subsequent runs of the NER model then used our hand-made entity disambiguations. This enables SpaCy to identify a large number of the pseudonyms and aliases and their locations within each section of the text.

\subsection{Challenges and Considerations} \label{challenges-and-considerations}

\subsubsection{Pronoun Coreferences}
One major problem with the Matcher approach is the extensive use of pronoun coreferences. We do not mitigate this.

Similarly, dialog presents a challenge in identifying named entities since the identity of the speaker often is often unstated. For example, in the following quote, two characters never explicitly mention each other but are refering to the same character, Bob.

\begin{displayquote}
``\emph{\underline{I}} am really concerned about \emph{\underline{Bob}}"\\
``\emph{\underline{I}} am concerned about \emph{\underline{him}} too."\\
``What should \underline{\emph{we}} do about \underline{\emph{his}} problem?"
\end{displayquote}

This exchange would be overlooked by our approach. While there are some approaches for coreference resolution at this granularity, most are trained on models not well suited for the unstructured and informal style of David Foster Wallace's novel. 

As such, the use of named entities as nodes, and our methodology for identifying where they exist in text, enables the generation of a co-mention network. However, such a network may not perfectly capture true latent interaction structure of the book.

\subsubsection{Point of View Sections}
Several sections in the book are written in the first person but, as the first person ``I'' is not a named entity (in the sense of being a proper noun), our matcher does not identify the narrating character as an entity in the scene. For example, in the second section, where Hal talks about eating mold, our matcher fails to find him.

One solution to this would be to manually annotate the sections that are in the first person point of view with their narrator. With that information, it would be possible to replace first person pronouns with the character's name, but such an approach would need to do so only outside of dialogue. We do not do so in this work.

\subsubsection{Reference versus Interaction}
Our approach makes no effort do differentiate between \textit{reference} and \textit{interaction}. This makes it a co-mention network and not one of interaction.

\subsubsection{False Positives}
We currently do not scope our entity matcher to a given section, so an alias or pseudonym for a character is applied uniformally to the whole book. For example, in the first section, Hal states:

\begin{displayquote}
I have been coached for this like a Don before a RICO hearing. 
\end{displayquote}

We match ``Don'' to Donald Gately, but in this instance, it is clear that Hal is not refering to him. A solution would be scope entity matches to sections, but we have not done this.

\subsubsection{Disambiguation}
Our matcher has no way of differentiating between two characters with the same name. Generally, we deal with this by not matching on that name -- for instance, `Incandenza' does not match to James, Orin, Mario, Avril, or Hal, as we are unable to determine who is being referenced. Entity scoping to sections would ameliorate, but not solve, this problem.

\subsubsection{Hypergraph: a single match refering to multiple characters}
``\ldots~the Vaught twins are heading down the hall to the bathroom at the far end\ldots'' (\infinitejest, section 159) Though the Vaught twins refers to Sharyn and Caryn Vaught (obviously -- who could forget the Vaught twins?) our matcher does not pick up an entity from this sentence, as we have no mechanism for one ``match'' to indicate more than one character. Philosophically, this is perhaps the most glaring hole in our approach.

\subsubsection{Pseudonyms}
We treat pseudonyms as references to the pseudonymous individual. This is \textit{certainly} inappropriate, but seemed more appropriate to us than ignoring the reference entirely. As an example, Joelle van Dyne hosts a radio show under the pseudonym ``Madame Psychosis''; when a character mentions Madame Psychosis, we count that as a reference to Joelle van Dyne, despite the fact that the connection between the two -- Joelle van Dyne and Madame Psychosis -- is not common knowledge and is unlikely to be known to the mentioner.

There are several solutions to this problem. One would be to represent pseudonyms as separate entities, though this has unappealing downsides (like failing to associate mentions of the pseudonym with the real entity when the pseudonym mentioner is aware of the pseudonym ``bearer's'' real entity). Another would be to make a directed edge for certain matches, but this would require inferring the directionality of such mentions, which we cannot do without significantly deeper understanding of the text.
